Paper_stuff

### 2023-09-14 Depression_Vis.Rmd
Adding anxiety / depression by duration

```{r}
Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

#Create a Time Variable
Mothership_Long$TxDay <- NA
Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20

#Create a New Data Set with an Average Anxiety Variable
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
```

>>>>

```{r}
Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]

#Create a Time Variable
Mothership_Long_dep$TxDay <- NA
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day11_CUDOS"]<-11
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day12_CUDOS"]<-12
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day13_CUDOS"]<-13
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day14_CUDOS"]<-14
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day15_CUDOS"]<-15
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day16_CUDOS"]<-16
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day17_CUDOS"]<-17
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day18_CUDOS"]<-18
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day19_CUDOS"]<-19
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day20_CUDOS"]<-20

#Create a New Data Set with an Average Anxiety Variable
Mothership_Mean_CUDOS<-Mothership_Long_dep %>%
  group_by(TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
```

### 2023-09-14 Paper_stuff.Rmd
Adding anxiety / depression by duration

ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4300))+
  coord_flip()
```

@@

Mothership_current_Imp <- Mothership_Diag_treat %>%
  pivot_longer(
    cols=c("Co_Anx","Co_Mood","Co_OCD","CO_BPD","CO_Psychotic","CO_Eating","CO_Somatic", "CO_Substance","CO_Trauma", "No_Co"),
    names_to = 'Disorder_Present') %>%
  filter(value != 0) %>%
  select(!value)  %>%
  filter(!is.na(Disorder_Present))%>%
  filter(!is.na(Disorder_treat))

co_dis_tab <- Mothership_Diag_treat |>
  pivot_longer(
    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "CO_Substance","Co_Trauma", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat))

@@

p <- Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .75)+
 scale_size_area(max_size = 30)+
  scale_colour_manual(values = c("#FE6CAA","#f7a174","#B1D4E0","#A06CFE","red"))+
  #scale_size_continuous(range = c(10, 30)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Other_Co" = "Other",
                            "No_Co" = "None",
                            "BPD_Co_C" = "BPD",
                            "Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Mood_C" = "Mood",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis")

•	Visualizations – CUDOS and CUXOS trajectories by treatment duration, treatment track, most common diagnoses. 
•	Visualization – RDQ pre and post change.
•	Table or Visualization – Reasons for discharge results.

>>>>

ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4300))+
  coord_flip()

ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,2000))+
  coord_flip()+
  facet_wrap(~Duration)
```

@@

Mothership_current_Imp <- Mothership_Diag_treat %>%
  pivot_longer(
    cols=c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
    names_to = 'Disorder_Present') %>%
  filter(value != 0) %>%
  select(!value)  %>%
  filter(!is.na(Disorder_Present))%>%
  filter(!is.na(Disorder_treat))

co_dis_tab <- Mothership_Diag_treat |>
  pivot_longer(
    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat))

@@

p <- Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .75)+
 scale_size_area(max_size = 30)+
  scale_colour_manual(values = c("#ffa600","#ff6361","#bc5090","#58508d","#003f5c"))+
  #scale_size_continuous(range = c(10, 30)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Other_Co" = "Other",
                            "No_Co" = "None",
                            "BPD_Co_C" = "BPD",
                            "Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Mood_C" = "Mood",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis")

p
```

•	Visualizations – CUDOS and CUXOS trajectories by treatment duration, treatment track, most common diagnoses.

### plot means based upon duration group membership 
•	Visualization – RDQ pre and post change.
•	Table or Visualization – Reasons for discharge results.
